Probing the inner kpc of massive galaxies with strong gravitational lensing

### 2014-11-06 ms.tex
modifying everything
adding fig 5
PJM acknowldgements

\section{Conclusion}
We have examined the prospects of detecting central, demagnified images of strongly lensed molecular lines with ALMA. We found that there is a non-negligible space of realistic and plausible parameters that result in a high significance detection of the central images. We showed that such deep observations can either allow a measurement of the mass of the central SMBH and the stellar core size, or place strong limits on them.
We also studied the possibility of detecting binary SMBHs and found that only under very rare conditions central images may allow detection of both SMBHs.

\acknowledgements{
\red{Acknowledge NSF?}}

>>>>

\section{Conclusions}
We have examined the prospects of detecting central, demagnified images of strongly lensed molecular lines with ALMA. We found that there is a non-negligible space of realistic and plausible parameters that result in a high significance detection of the central images. We showed that such deep observations can either allow a measurement of the mass of the central SMBH and the stellar core size, or place strong limits on them.
We also studied the possibility of detecting binary SMBHs and found that only under very rare conditions central images may allow detection of both SMBHs.

\acknowledgements{
We thank Risa Wechsler and Matt Becker for interesting discussions.
\red{YH acknowledges support from the NSF ...}
The work of PJM was supported in part by the U.S.
Department of Energy under contract number DE-AC02-76SF00515.
}
